Analysis for Non-Expressive performances (DURATION)

### 2020-04-08 material/analysis/stim_n/ioi_duration.Rmd
change data.table name
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r normDus, include = FALSE}
# extract trials which have both onset and offset data
df_onset$Eval <- "NA"
for (subnr in unique(df_offset$SubNr)){
  for (trial in unique(df_offset[SubNr == subnr]$Trial)){
    df_onset[SubNr == subnr & TrialNr == trial]$Eval <- "Yes"
  }
}
df_ioi <- df_onset[Eval == "Yes"]

# check whether each row corresponds correctly
df_ioi$Eval2 <- "NA"
for (i in 1:nrow(df_ioi)){
  if (df_ioi[i]$SubNr == df_offset[i]$SubNr & df_ioi[i]$TrialNr == df_offset[i]$TrialNr & df_ioi[i]$Pitch == df_offset[i]$Pitch){
    df_ioi[i]$Eval2 <- "SAME"
  } else {
    df_ioi[i]$Eval2 <- "DIFF"
  }
}
print(unique(df_ioi$Eval2))

# calculate duration
df_ioi$Duration <- df_offset$TimeStamp - df_ioi$TimeStamp

# convert bpm to ms
df_ioi[Tempo == 120]$Tempo <- 250
df_ioi[Tempo == 110]$Tempo <- 273
df_ioi[Tempo == 100]$Tempo <- 300

# normalised Duration
df_ioi$normDu <- df_ioi$Duration/df_ioi$Tempo

# remove irrelevant intervals
ls_irrelevant <- list(c(27:28), c(33:35), 52, 57, c(66:72))
df_ioi$EighthNote <- "Yes"

for (phrase in 1:length(ls_irrelevant)){
  for (note in 1:length(ls_irrelevant[[phrase]])){
    df_ioi[RowNr == ls_irrelevant[[phrase]][note]]$EighthNote <- "No"
  }
}
```

@@

```{r ioi, echo = FALSE}
# For each individual
ioi <- df_ioi[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), by = .(SubNr)]
print(ioi)
```

@@

```{r ioi_bar,  echo = FALSE}
p_ioi <- ggplot(data = ioi, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  labs(y = "Normalised Duration", subtitle = "Duration: Non-Expression")
p_ioi
```

## Sequence plot
```{r seq, fig.width = 10, echo = FALSE}
# For each individual
ioi_seq <- df_ioi[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), .(SubNr, RowNr)]

p_ioi_seq <- ggplot(data = ioi_seq, aes(x = RowNr, y = Mean, colour = SubNr)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width=.2,
                position = position_dodge(.05)) + 
  labs(x = "RowNr", y = "Normalised Duration") + scale_x_continuous(breaks=seq(1,66,1))
p_ioi_seq
```

@@

```{r ioi_all, echo = FALSE}
# Group mean
ioi_all <- df_ioi[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu))]
print(ioi_all)
```

## Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < mean(ioi$Mean)+3*mean(ioi$SD) & Mean > mean(ioi$Mean)-3*mean(ioi$SD)]
print(excluded_ioi)
```

```{r export, include = FALSE}
# export df_ioi
write.csv(df_ioi, file = "./data_duration.csv", row.names = F)
```

>>>>

```{r normDus, include = FALSE}
# extract trials which have both onset and offset data
df_onset$Eval <- "NA"
for (subnr in unique(df_offset$SubNr)){
  for (trial in unique(df_offset[SubNr == subnr]$Trial)){
    df_onset[SubNr == subnr & TrialNr == trial]$Eval <- "Yes"
  }
}
df_duration <- df_onset[Eval == "Yes"]

# check whether each row corresponds correctly
df_duration$Eval2 <- "NA"
for (i in 1:nrow(df_duration)){
  if (df_duration[i]$SubNr == df_offset[i]$SubNr & df_duration[i]$TrialNr == df_offset[i]$TrialNr & df_duration[i]$Pitch == df_offset[i]$Pitch){
    df_duration[i]$Eval2 <- "SAME"
  } else {
    df_duration[i]$Eval2 <- "DIFF"
  }
}
print(unique(df_duration$Eval2))

# calculate duration
df_duration$Duration <- df_offset$TimeStamp - df_duration$TimeStamp

# convert bpm to ms
df_duration[Tempo == 120]$Tempo <- 250
df_duration[Tempo == 110]$Tempo <- 273
df_duration[Tempo == 100]$Tempo <- 300

# normalised Duration
df_duration$normDu <- df_duration$Duration/df_duration$Tempo

# remove irrelevant intervals
ls_irrelevant <- list(c(27:28), c(33:35), 52, 57, c(66:72))
df_duration$EighthNote <- "Yes"

for (phrase in 1:length(ls_irrelevant)){
  for (note in 1:length(ls_irrelevant[[phrase]])){
    df_duration[RowNr == ls_irrelevant[[phrase]][note]]$EighthNote <- "No"
  }
}
```

@@

```{r duration, echo = FALSE}
# For each individual
duration <- df_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), by = .(SubNr)]
print(duration)
```

@@

```{r duration_bar,  echo = FALSE}
p_duration <- ggplot(data = duration, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  labs(y = "Normalised Duration", subtitle = "Duration: Non-Expression")
p_duration
```

## Sequence plot
```{r seq, fig.width = 10, echo = FALSE}
# For each individual
duration_seq <- df_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), .(SubNr, RowNr)]

p_duration_seq <- ggplot(data = duration_seq, aes(x = RowNr, y = Mean, colour = SubNr)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width=.2,
                position = position_dodge(.05)) + 
  labs(x = "RowNr", y = "Normalised Duration") + scale_x_continuous(breaks=seq(1,66,1))
p_duration_seq
```

@@

```{r duration_all, echo = FALSE}
# Group mean
duration_all <- df_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu))]
print(duration_all)
```

## Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_duration <- duration[Mean < mean(duration$Mean)+3*mean(duration$SD) & Mean > mean(duration$Mean)-3*mean(duration$SD)]
print(excluded_duration)
```

```{r export, include = FALSE}
# export df_duration
write.csv(df_duration, file = "./data_duration.csv", row.names = F)
```
